`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-19 inst/manuscript/manuscript.rmd
Add a first draft on the traces plotting function;

##Graphic Representation of Spectral Traces
```{r, code = formatR::usage('scramblaseAssayTraces'), eval = FALSE}
```

>>>>

##Graphic Representation of Spectral Traces
In a first, graphical data analytics step of a scramblase assay-derived data 
set, fluorescent spectra or traces may be plotted in publication-appropriate
quality with acquisition time in the x- and fluorescense intensity on the y-axis
using
```{r, code = formatR::usage('scramblaseAssayTraces'), eval = FALSE}
```
and handing the function the path to the user assembled spreadsheet of input 
data (`x`). The `adjust` argument to the function call serves to selectively 
inactivate `wmtsa`-provided (see above) alignment of multiple spectra to the 
time of dithionite addition. Acquisition time coverage of the plot may be tuned 
by user-provided minimal (`timeMin` ) and maximal (`timeMax`) time points to be
included.
